% resume.tex - The Professional Resume of Adam A.G. Shamblin
\documentclass[11pt]{article}
\usepackage{times}

\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\marginparwidth=0.5in

\begin{document}

\title{Professional Resume}
\author{Adam A.G. Shamblin}
\date{December 2019}
\maketitle

\section*{Overview}
As a polyglot web application developer, I have had the opportunity to work in
a large number of languages on many platforms. I love the dynamic languages and
Unix-like environments where I've grown and cut my teeth. Even after all these
years in the industry, I'm still excited by the possibilities of the web, where
I feel there is plenty of space yet to be explored.

As a Director and Development Manager I lead and grew large cross-functional
teams of engineers and developers in the Financial and Healthcare sectors. I
found success leading teams to greater efficiency while rapidly growing the
depth and breadth of skills across the team. I reduced turnover on my teams by
focusing on team identity and encouraging every team member to participate and
to own our shared narrative.

Whether as a manager or as a senior contributor, I make teams better.

\section*{Experience}

\subsection*{Senior Software Architect at PGi}
\emph{April 2018 - Present}
\begin{itemize}
  \item Evaluate and introduce new development tools and techniques
  \item Participate in design discussions and code reviews
  \item Collaborate with Product and Engineering teams on strategic initiatives
  \item Provide ambient support to developers and teams on the ground
  \item Actively advocate for security within the engineering team
\end{itemize}
As a software architect at PGi, it is my responsibility to be a part of every
engineering team. Rather than dictate system design from an ivory tower, my
approach has been to work directly with teams, embedding when possible, to
arrive at the best implementation possible using the capabilities, time and
expertise at hand.
\textbf{Technology stack:} Kubernetes, Kubeless, NGINX, Kazoo Voip Platform, API Gateways

\subsection*{Senior Software Engineer at PGi/ReadyTalk}
\emph{October 2017 - April 2018}
\begin{itemize}
  \item Key contributor and architect to PGi's UCaaS desktop development effort
  \item Developed PGi flagship personal web conferencing application in Electron and Angular
  \item Frequent advisor to product efforts
  \item Founded and co-chaired the ReadyTalk Security Guild
  \item Recipient September 2018 Mediallion Programme award
\end{itemize}
Working directly with the Chief Architect and key partners, spearheaded the
development and integration of the Globalmeet Unified Communications (UC)
product. Guided development of the product across multiple teams and timezones
under very aggressive timelines.
\textbf{Technology stack:} Angular5+, Node.js, Typescript Electron, Kanban

\subsection*{Lead Full-Stack Developer/Acting Director of Security at ThinkTank}
\emph{January 2017 - October 2018}
\begin{itemize}
  \item Lead and mentored a cross-functional team of developers, testers and product managers to plan, develop and deploy the ThinkTank flagship application.
  \item Worked with CFO and Product Management to establish, review and ratify the total of ThinkTank's security policies.
  \item Negotiated and consolidated security software contracts, resulting in ~25k annual software and contractor savings.
\end{itemize}
\textbf{Technology stack:} Angular2/4, Node.js, Docker, Amazon AWS (ECS, S3, Inspector), Typescript, Veracode, AlertLogic, Bash, Python

\subsection*{Senior Cloud Front End Developer at Hewlett Packard Enterprise}
\emph{August 2015 - December 2016}
\begin{itemize}
  \item Contributed to the development of the HP Helion Eucalyptus Cloud Management Console.
  \item Advocated for stronger web design patterns by demonstrating effective use of AngularJS directives, services, and by introducing more solid REST principles.
  \item Provided feedback to documentation team to improve user experience.
  \item Administered a small, two-node HP Eucalyptus cloud in my home office for testing and deployment of web projects.
  \item Participated in a maturing agile/scrum process among an entirely distributed team.
\end{itemize}
\textbf{Technology stack:} AngularJS, Python, Pyramid, boto, d3.js, Foundation, HP Helion Eucalyptus, Amazon AWS, CentOS, gunicorn, SASS, bash, IRC

\subsection*{Senior Web Engineer at MapQuest}
\emph{September 2014 - August 2015}

\subsection*{Director of Application Development at Datu Health}
\emph{May 2013 - December 2013}

\subsection*{Director, Development Manager at Markit On Demand}
\emph{August 2009 - May 2013}

\section*{Training and Awards}

\end{document}
